A spiral galaxy's mass distribution uncovered through lensing and dynamics

### 2015-08-13 docs/results_JAMwithSB_v1.01.tex
Started writing data section.
Started writing section on JAM modelling with surface brightness MGE. Updated plot on model G enclosed mass.

\subsubsection{... with "Mass-follows-Light" and Velocity Anisotropy}

@@

\begin{figure*}
\centering
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[height=6cm]{fig/jam_A2_vrms.ps}
  \caption{??? Preliminary crappy caption: Failed try to fit a mass-follows-light model to the central regions of the galaxy. "Best fit" velocity anisotropy $\beta = -1/2$ is pegged at lower limit. ??? [TO DO: nice caption]}
  \label{fig:???}
\end{minipage}%
\begin{minipage}{.5\textwidth}
  \centering
  \includegraphics[height=6cm]{fig/lensing_JAM_comparision.ps}
  \caption{??? Preliminary crappy caption: Observed vrms is overplotted (not fitted) with best fit lens mass models for $\alpha = 1$ (red) and $\alpha = 1.1$ (green).??? [TO DO: nice caption]}
  \label{fig:???}
\end{minipage}
\end{figure*}

\subsubsection{... with Increasing Mass-to-Light Ratio Gradient}

@@

\subsubsection{... with the Lens Mass Model}

>>>>

\paragraph{... with the Lens Mass Model.} Our first JAM model uses the mass distribution which we found from lensing constraints in \S\ref{sec:results_lensing} to generate an independent prediction for the $v_\text{rms}$ curve following the procedure in \S\ref{sec:model_JAM}. In addition to the flat rotation curve model with $\alpha = 1$ in Table \ref{tab:bestfitlensmodel}, we also investigate a lens model, which was found as a best fit to the lensing images when assuming a [TO DO: rising or droppint???] rotation curve slope of $\alpha=1.1$. The predictions are compared with the data in Figure \ref{fig:JAM_modelL}. The agreement between the lensing prediction and the observed kinematics within $R' \sim 3$ arcsec is striking, especially around the Einstein radius. The $\alpha = 1$ model fits the wings nicely, while the $\alpha = 1.1$ model recreates almost exactly the observed central dip. The sharp drop in $v_\text{rms}$ around $R' \sim 3$ arcsec [TO DO: make sure all projected Rs are $R'$] cannot be reproduced, however. But outside of the Einstein radius our lensing models are only extrapolations and the true constraint is around the Einstein radius.

%==================================================================

\begin{figure}
  \centering
  \includegraphics[height=6cm]{fig/lensing_JAM_comparision.ps}
  \caption{Comparison (not a fit!) of the symmetrized stellar $v_\text{rms}$ data of J1331 (blue dots) with JAM models generated from mass distributions which were independently derived from lensing constraints in \S\ref{sec:results_lensing}. The red solid line corresponds to the lens model for a flat rotation curve ($\alpha = 1$) in Table \ref{tab:bestfitlensmodel}; the green line is a best fit lens model found analogously from the image positions, but for a fixed rotation curve slope of $\alpha = 1.1$. For the JAM modelling a best fit MGE to the lens mass models were used, as well as the observed surface brightness MGE in Table \ref{tab:MGEF814W}, assuming velocity isotropy $\beta_z = 0$ and an inclination of $i = 70^\circ$.The red and black dotted lines are the Einstein radius and the effective half-light radius, respectively.}
  \label{fig:JAM_modelL}
\end{figure}

%==================================================================

\paragraph{... with "Mass-follows-Light" and Velocity Anisotropy.} Our second JAM model is a mass-follows-light model, which are often used in dynamical JAM modelling (e.g. \citet{GlennEC,Cap06}), where the mass distribution ins generated by multiplying the light distribution in Table \ref{tab:MGEF814W} by a constant total mass-to-light ratio  $\Upsilon_{I,\text{tot}}^\text{dyn}$. This assumes that the dark matter is always a constant fraction of the total matter distribution everywhere. This simplified model sometimes gives good representations of the inner parts of galaxies, where the stellar component dominates. In addition to the free fit parameter  $\Upsilon_{I,\text{tot}}^\text{dyn}$, we also allow for a overall constant but non-zero velocity anisotropy $\beta_z$. The best fit is found by minimizing $\chi^2$ between the $v_\text{rms}$ data and model prediction and is demonstrated in Figure \ref{fig:JAM_modelA2}. For $\beta_z$ we impose the fitting limits $\beta_z \in [-0.5,+0.5]$. While the outer parts of galaxies often show radially biased velocity anisotropy up to $\sim 0.5$ (from dynamical modelling of observed elliptical galaxies (e.g. \citet{Kronawitter2000}) and cosmological simulations (e.g. \citet{2004MNRAS.352..535D,2001ApJ...557..533F}), the centers of galaxies are near-isotropic or have  negative velocity anisotropy \citep{2003ApJ...583...92G}. Only in extreme models (e.g. around in-spiralling supermassive black holes \citep{1997NewA....2..533Q}) velocity anisotropies as low as $\sim -1$ have been found. A lower limit of $\beta_z \geq -0.5$ is a realistic assumption for J1331, for which we do not expect extreme dynamical conditions. The best fit in Figure \ref{fig:JAM_modelA2} however strives to very negative velocity anisotropies to be able to get the deep central dip in the  $v_\text{rms}$ curve. But $\beta_z = -0.5$ is not even a remotely agreeable fit and lower anisotropies are not to be expected and realistic. We also tested radial profiles for $\beta_z(R)$ of the form proposed by \citet{BaesVanHese}, which was however equally unable to reproduce the data. We conclude, that this is due to the well-known degeneracy between anisotropy and mass profile [TO DO: REF] and the mass-follows-light model is \emph{not} a good representation of the mass distribution in J1331's inner regions.

%==================================================================

\begin{figure}
  \centering
  \includegraphics[height=6cm]{fig/jam_A2_vrms.ps}
  \caption{Comparison of the symmetrized $v_\text{rms}$ data of J1331 (blue dots) with a best fit dynamical JAM model (solid red line) assuming mass-follows-light and with two free parameters: $\Upsilon_{I,\text{tot}}^\text{dyn}$, the total I-band mass-to-light ratio found from dynamics, which converts the observed surface brightness in Table \ref{tab:MGEF814W} into a mass distribution, and the velocity anisotropy parameter $\beta_z$. The "best" fit is $\Upsilon_{I,*}^\text{dyn} = 4.8 \pm 0.1$ and $\beta_z = -0.5$, where the latter is however pegged at the lower limit of the allowed value range. This is obviously not a good model.}
  \label{fig:JAM_modelA2}
\end{figure}

%==================================================================

\paragraph{... with Increasing Mass-to-Light Ratio Gradient.} In \S\ref{sec:results_lensing} we found from the lensing, that the light distribution might drop faster with radius than the mass distribution. This would correspond to a radially increasing total mass-to-light ratio. As velocity anisotropy alone cannot explain the observed kinematics in a simple a mass-follows-light model, we now allow for an increasing mass-to-light ratio gradient in the JAM modelling to generate a mass model from the light distribution in Table \ref{tab:MGEF814W}. We do this by assigning each of the five Gaussians in the MGE its own mass-to-light ratio and replace the total luminosity in Eq. (\ref{eq:centralItotalL}) $L_i$ with the Gaussians total Mass $M_i = \Upsilon_{i} L_i$. We treat the five $\Upsilon_i$ as free parameters and only require that $\Upsilon_{j} \geq \Upsilon_i$ when the corresponding $\sigma_j \geq \sigma_i$ to ensure an overall mass-to-light ratio that is increasing with radius. [TO DO: Discuss Figure]

@@

%==================================================================

@@

%==================================================================
